Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-17 main.tex
Uni Kassel affiliation + ERC

\author[irccyn]{Maxime Folschette}
\ead{Maxime.Folschette@irccyn.ec-nantes.fr}
\author[lri]{Loïc Paulevé}
\author[irccyn]{Morgan Magnin}
\author[irccyn]{Olivier Roux}

@@

@@

>>>>

\author[irccyn,unikassel]{Maxime Folschette}
\ead{Maxime.Folschette@irccyn.ec-nantes.fr}
\author[lri]{Loïc Paulevé}
\author[irccyn]{Morgan Magnin}
\author[irccyn]{Olivier Roux}

@@

\address[unikassel]{School of Electrical Engineering and Computer Science,\\
  University of Kassel, Germany}

@@

{\small
\paragraph{Acknowledgement}
The European Research Council has provided financial support
under the European Community's Seventh Framework Programme (FP7/2007--2013)~/
ERC grant agreement no.~259267.
}
